Tweets

### 2020-05-20 Rmd/tweets-one.Rmd
added files produced from tweets analysis

```{r}
tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), 
                   col_names = FALSE)
```

@@

```{r}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
```

@@

```{r}
ids <- readr::read_csv(paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```

```{r}
# save ids of tweets that we actually used
readr::write_csv(tweets_rehydrated$status_id, path = paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv"), col_names = FALSE)
```

@@

```{r}
# create a twitter-specific stop word list
remove_reg <- "&amp;|&lt;|&gt;"
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

```{r}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
# https://www.tidytextmining.com/twitter.html
word_counts <- tweets_rehydrated %>% 
  dplyr::filter(lang == "en") %>%
  dplyr::filter(!stringr::str_detect(text, "^RT")) %>%
  dplyr::mutate(text = stringr::str_remove_all(text, remove_reg)) %>%
  tidytext::unnest_tokens(output = word, input = text) %>%
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```

```{r}
tweets_dtm <- word_counts %>%
  tidytext::cast_dtm(status_id, word, n)
```

```{r}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 10)
```

```{r}
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

```{r}
tweets_top_terms <- tweets_beta %>%
  dplyr::group_by(topic) %>%
  dplyr::top_n(10, beta) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(topic, -beta)
```

```{r}
tweets_top_terms %>%
  dplyr::mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip()
```

```{r}
tweets_gamma <- tidytext::tidy(tweets_lda, matrix = "gamma")
tweets_gamma
```

```{r, eval = FALSE}
# too many documents to plot all
tweets_gamma %>%
  dplyr::mutate(title = reorder(document, gamma * topic)) %>%
  ggplot2::ggplot(ggplot2::aes(factor(topic), gamma)) +
  ggplot2::geom_boxplot() +
  ggplot2::facet_wrap(~ document)
```

```{r}
Sys.sleep(15 * 60) # sleep for 15 minutes to allow api limits to reset
```

>>>>

```{r, recover-{{date}}}
tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), 
                   col_names = FALSE)
```

@@

```{r, broken-{{date}}}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
```

@@

```{r, ids-{{date}}}
ids <- readr::read_csv(paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```

```{r, saveids-{{date}}}
# save ids of tweets that we actually used
readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv"), col_names = FALSE)
```

@@

```{r, stops-{{date}}}
# create a twitter-specific stop word list
remove_reg <- "&amp;|&lt;|&gt;"
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

```{r, wordcounts-{{date}}}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
# https://www.tidytextmining.com/twitter.html
word_counts <- tweets_rehydrated %>% 
  dplyr::filter(lang == "en") %>%
  dplyr::filter(!stringr::str_detect(text, "^RT")) %>%
  dplyr::mutate(text = stringr::str_remove_all(text, remove_reg)) %>%
  tidytext::unnest_tokens(output = word, input = text) %>%
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```

```{r, cast-{{date}}}
tweets_dtm <- word_counts %>%
  tidytext::cast_dtm(status_id, word, n)
```

```{r, lda-{{date}}}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 8)
```

```{r, beta-{{date}}}
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

```{r, topterms-{{date}}}
tweets_top_terms <- tweets_beta %>%
  dplyr::group_by(topic) %>%
  dplyr::top_n(10, beta) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(topic, -beta)
```

```{r, plot-{{date}}}
tweets_top_terms %>%
  dplyr::mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip()
```

```{r, gamma-{{date}}}
tweets_gamma <- tidytext::tidy(tweets_lda, matrix = "gamma")
tweets_gamma
```

```{r, sleep-{{date}}}
Sys.sleep(15 * 60) # sleep for 15 minutes to allow api limits to reset
```
